A holographic approach to the six-dimensional superconformal index

### 2023-03-22 fivebranes/fact.tex
merge

At the level of $\infty$-jets the the decomposition in equation \eqref{eqn:Gdecomp} induces a weight grading of $\Hat{E(5|10)}$ which extends the one on $E(5|10)$ that we just described by declaring that the central term have weight $-1$.
In this way, we get a related decomposition of super $L_\infty$ algebras
\beqn\label{eqn:decomp2}
\Hat{E(5|10)} = \prod_{n \geq -1} V_n
\eeqn
We will refer to this as the \textit{fivebrane decomposition} of $\Hat{E(5|10)}$.
Here $V_{-1}$ is a $\C$-extension of $\til V_{-1}$ defined in the decomposition \eqref{eqn:decomp1}.
Notice that for $n \geq 0$ the $V_n$'s are the same as in the non centrally extended case.

>>>>

      v n                  
At the level of $\infty$-jets the the decomposition in equation \eqref{eqn:Gdecomp} induces a weight grading of $\Hat{E(5|10)}$ which extends the one on $E(5|10)$ that we just described by declaring that the central term have weight $-1$.
In this way, we get a related decomposition of super $L_\infty$ algebras
\beqn\label{eqn:decomp2}
\Hat{E(5|10)} = \prod_{n               \geq -1} V_n            
\eeqn                      
We will refer to this as the \textit{fivebrane decomposition} of $\Hat{E(5|10)}$.
Here $V_{-1}$ is a $\C$-extension of $\til V_{-1}$ defined in the decomposition \eqref{eqn:decomp1}.
Notice that for $n \geq 0$ the $V_n$'s are the same as in the non centrally extended case.
